---
title: "Covid-19 Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: ["twitter","facebook","menu"]
    source_code: embed
    theme: cosmo
---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(dplyr)
library(openintro)
library(highcharter)
library(ggvis)
```

```{r}
data<-read.csv("C:/Users/Bhavik/Desktop/Data Science/Other/Covid-19.csv")
```

```{r}
mycolors<-c("blue","#FFC125","darkgreen","darkorange")
```

Interactive Data Visualization
===================================== 

Row
-------------------------------------

### Covid-19 Analysis

```{r}
valueBox(paste("Covid-19"),
         color = "warning")
```

### Total Infected

```{r}
valueBox(sum(data$Total.Cases),
         icon = "fa-bug")
```

### New Infected Cases

```{r}
valueBox(sum(data$New.Cases),
         icon = "fa-ambulance")
```

### Total Deaths 

```{r}
valueBox(sum(data$Total.Deaths),
         icon = "fa-skull")
```

### Total Recovered

```{r}
valueBox(sum(data$Total.Recovered),
         icon = "fa fa-heartbeat")
```

### Active Infected

```{r}
valueBox(sum(data$Active.Cases),
         icon = "fa-plus-square")
```

Row
-------------------------------------

### Top Highest Number of Covid-19 Infected Countries

```{r}
y1<-data$Total.Cases[data$Total.Cases>1000]
x1<-data$Country[data$Total.Cases>1000]
x1<-as.character(x1)
xy<-data.frame(x1,y1)
xy$x1<-factor(xy$x1,levels = unique(xy$x1)[order(xy$y1,decreasing = T)])
p3 <-plot_ly(xy,
              x = ~x1,
              y = ~y1,
              text = paste("Country:", xy$x1,
                           "Total.Cases:", xy$y1),
              type = "bar") %>%
  layout(xaxis = list(title="Countries"),
         yaxis = list(title = "Total.Cases"))
p3


```

### Covid-19 Percentage of Death, Recovered and Active Cases

```{r}

x<-c(sum(data$Total.Deaths),
     sum(data$Total.Recovered),
     sum(data$Active.Cases))
Category<-c("Total Deaths","Total Recovered","Active Cases")
xy<-data.frame(x,Category)
p2 <- xy %>%
  group_by(Category) %>%
  summarise(sum = x) %>%
  plot_ly(labels = ~Category,
          values = ~sum,
          marker = list(colors = c("lightblue","coral","lightgreen"))) %>%
  add_pie(hole = 0.2) %>%
  layout(xaxis = list(zeroline = F,
                      showline = F,
                      showticklabels = F,
                      showgrid = F),
         yaxis = list(zeroline = F,
                      showline = F,
                      showticklabels=F,
                      showgrid=F))
p2
```


### Comparision of Death against Recovery of Top Countries

```{r}

barplot_data1<-data$Total.Deaths[data$Total.Deaths>500]
barplot_data2<-data$Total.Recovered[data$Total.Deaths>500]
Countries<-as.character(data$Country[data$Total.Deaths>500])
xyz<-data.frame(Countries,barplot_data1,barplot_data2)
xyz$Countries<-factor(xyz$Countries,levels = unique(xyz$Countries)[order(xyz$barplot_data1,decreasing = T)])

p3 <- plot_ly(xyz,
              x = ~Countries,
              y = ~barplot_data1,
              type = "bar",
              name = "Death") %>% 
  add_trace(y = ~barplot_data2,
            name = "Recovered") %>% 
  layout(yaxis = list(title = "Cases"),
         barmode = "group")
p3

```

Map
========================================

### World Map

```{r}
cases <- data %>%
  group_by(CountryName) %>%
  summarize(total=first(Total.Cases))

highchart() %>%
  hc_title(text = "Corona Infected Cases in the World") %>%
  hc_subtitle(text = "Source: Covid-19.csv") %>%
  hc_add_series_map(worldgeojson, cases,
                    name = "CountryName",
                    value = "total",
                    joinBy = c("name", "CountryName")) %>%
  hc_mapNavigation(enabled = T)
```

Data Table
========================================

```{r}
datatable(data,
          caption = "Covid-19 Data",
          rownames = T,
          filter = "top",
          options = list(pageLength = 25))
```

Pivot Table
=========================================

```{r}
rpivotTable(data,
            aggregatorName = "Sum",
            cols= "Total",
            rows = c("CountryName","Total.Deaths","Total.Recovered","Active.Cases","Total.Cases"),
            rendererName = "Heatmap",
            vals = c("Total.Cases"))
            
```

Summary {data-orientation=columns}
===========================================

Column
-----------------------------------

### Total Deaths Around The World

```{r}
valueBox(sum(data$Total.Deaths),
         icon = "fa-skull" )
```

### Max Number of Deaths 

```{r}
valueBox(max(data$Total.Deaths),
         icon = "fa-skull" )
```

### Average Death Per Day
```{r}
valueBox(round(mean(data$Total.Deaths),
               digits = 2),
         icon = "fa-skull")
```

### Average Recovered Per Day
```{r}
valueBox(round(mean(data$Total.Recovered),
               digits = 0),
         icon = "fa fa-heartbeat")
```

Column
---------------------------

Report

* This report is created for learning and education purpose only.

* This is a report on `r sum(data$Total.Cases)` Corona Cases identified.

* The average per day death was `r round(mean(data$Total.Deaths),0)`.

* The average per day recovered was `r round(mean(data$Total.Recovered),0)`.

This report was generated on `r format(Sys.Date(), format = "%B %d, %Y")`.

About Report
========================================

Disclaim: Strictly for Learning and Education only

Created by: Bhavik Dudhrejiya

Email ID: Bhavik.datascience@gmail.com

Data Source:https://www.worldometers.info/coronavirus/

Confidential: Low!
